First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-07-13 eg6-letters/coherent/dvcs_he4_prl.tex
Changes in ref for coherent submission to PRL

\bibitem{Burkardt:2000za} 
  M.~Burkardt,
  Phys.\ Rev.\ D {\bf 62}, 071503 (2000);
  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002).

@@

\bibitem{Freund_Collins}
A.~Freund and J.C.~Collins, 
Phys.\ Rev.\ D {\bf 59}, 074009 (1998).

@@

\bibitem{simonetta_2}
S.~Liuti and K.~Taneja, 
Phys.\ Rev.\ C {\bf 72}, 032201 (2005).

>>>>

\bibitem{Burkardt:2000za} 
  M.~Burkardt,
  Phys.\ Rev.\ D {\bf 62}, 071503 (2000);
  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903(E) (2002).

@@

\bibitem{Freund_Collins}
J.C.~Collins and A.~Freund, 
Phys.\ Rev.\ D {\bf 59}, 074009 (1999).

@@

\bibitem{simonetta_2}
S.~Liuti and S.K.~Taneja, 
Phys.\ Rev.\ C {\bf 72}, 032201 (2005).
